---
title: "Classwork/ Week4, Jorge"
author: "Jorge Arauz"
date: "2/2/2022"
output: word_document
---


Question #1
For the lists given below, show and use R code (a map function) to iteratively 
find the square of the sums across the vectors

```{r}
library(tidyverse)
a <- list(2, 4, 5, 9, 1)
b <- list(8, 7, 2, 8, 3)
c <- list(1, 8, 5, 4, 2)
```

```{r}
pmap_dbl(list(a,b,c), sum) -> question_1
question_1^2
```



Question #2
Using the data table below, use and show R code that will output a statement that
is descriptive for all rows of the data table.
The first row is given below.  Your code should produce the other specific statements.
  John who is Male, has a salary that is 65000 dollars per year.


```{r}
tribble( ~Student,  ~Gender,    ~Salary,
          "John",   "Male",       65000,
          "Alice",  "Female",    73000,
          "Juan",   "Male",       66000,
          "Beth",  "Female",    71500,
          "Denise", "Female",  82000
) -> table
table
```

```{r}
table %>% 
  pmap_chr(~ str_glue("{..1} who is a {..2}, has a salary that is {..3} dollars per year"))
```



Question #3
Write a nested loop that will produce a 5 by 5 matrix that whose matrix elements are sums of the corresponding columns and rows.

```{r}
matrix1 = matrix(nrow=5, ncol=5) # create a 5 x 5 matrix(5 rows and 5 columns)
for(i in 1:nrow(matrix1))        #// Assigned a variable 'i' for each row
{
  for(j in 1:ncol(matrix1))      #// Assigned a variable 'j' for each column
  {
    matrix1[i,j] = i+j           #// calculating product of two indeces
  }
}
print(matrix1)
```



Question #4
Use for loop coding to produce the number sequence shown below: Note that the numbers 5 and 10 are missing

1
2
3
4
6
7
8
9
11
12
13
14
15
16
17
18
19
20

```{r}
x <- 1:20
for (val in x) {
  if (val == 5){
    next
  }
  if (val == 10){
    next
  }
  print(val)
}
```







